Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-09 paper.tex
small typo fixes

\subsection*{Development model}
\texttt{Msprime} has a large number of features, encompassing
the functionality of several more specialised simulators
while maintaining excellent performance.
It is developed by a geographically distributed team of volunteers under an
open source community development model, with a strong emphasis
on code quality, correctness, good documentation, and inclusive development.
As in any large code base,
unit tests play a key role in ensuring that new additions behave
as expected and \msprime\ has an extensive suite.
As of the 1.0.0 release \msprime\ consists of around 13K lines of C and 11K
lines of Python, with suites of 122 C tests (7K lines of code) and
1350 Python tests (22K lines of code). These tests are run
automatically on different operating systems on each pull request
(where a contributor proposes a code change), using standard Continuous
Integration (CI) methodology. Other CI services check code formatting
and for common errors, as well as producing reports on the level of
test coverage, e.g., pinpointing areas where additional unit tests may
be required.

@@

% THERE IS A BETTER WAY!!!
Scientific software is vital apparatus, and must be engineered
to a high quality if we are to trust its results. There is a growing
realisation across the sciences \citet[OTHER CITATIONS]{siepel2019challenges}
% Maybe cite: https://www.biorxiv.org/content/10.1101/092205v3
that investing in
shared community infrastructure produces better results than a
proliferation of individually maintained tools, allowing scientists
to focus on their specific questions rather than software engineering.
\texttt{Msprime} 1.0 is the result of such a community process,
with features added by motivated users, taking advantage of the
established development practices and infrastructure.
% I'm going out on a limb here - do folks agree?
% PLR- personally I have learned SO MUCH, and I'm passing it on to others
Software development in a welcoming community,
with mentorship by experienced developers,
is a hugely useful experience for many users,
The skills that contributors learn
can lead to greatly increased productivity in subsequent
work (e.g., through more reliable code and better debugging skills).
We hope that users who find that
features they require are missing will continue to contribute to
\msprime, leading to a community project that is both high quality
and sustainable in the long term.

@@

\section*{Acknowledgements}
JK is supported by the Robertson Foundation.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
ADK was supported by NIH awards R01GM117241 and R01HG010774.
Franz Baumdicker is funded by the Deutsche Forschungsgemeinschaft
EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
BE was supported by  DFG grant  273887127 through Priority
Programme SPP 1819: Rapid Evolutionary Adaptation (grant STE 325/17-2) to Wolfgang Stephan; BE would also like to acknowledge  funding through The Icelandic Research
Centre (Rann{\'i}s) through an Icelandic Research Fund Grant of  Excellence nr.\ 185151-051 to Einar \'Arnason,  Katr\'in Halld\'orsd\'ottir,  Alison Etheridge,  Wolfgang Stephan, and BE.
Gregor Gorjanc is supported by the Chancellor's Fellowship of the University of
Edinburgh and the BBSRC grant to The Roslin Institute BBS/E/D/30002275.

>>>>

\subsection*{Development model}
\texttt{Msprime} has a large number of features, encompassing
the functionality of several more specialised simulators
while maintaining excellent performance.
It is developed by a geographically distributed team of volunteers under an
open source community development model, with a strong emphasis
on code quality, correctness, good documentation, and inclusive development.
As in any large code base,
unit tests play a key role in ensuring that new additions behave
as expected and \msprime\ has an extensive suite.
As of the 1.0.0 release \msprime\ consists of around 13K lines of C and 11K
lines of Python, with suites of 122 C tests (7K lines of code) and
1350 Python tests (22K lines of code). These tests are run
automatically on different operating systems on each pull request
(where a contributor proposes a code change), using standard Continuous
Integration (CI) methodology. Other CI services check code formatting
and for common errors, as well as produce reports on the level of
test coverage, e.g., pinpointing areas where additional unit tests may
be required.

@@

% THERE IS A BETTER WAY!!!
Scientific software is a vital apparatus, and must be engineered
to a high quality if we are to trust its results. There is a growing
realisation across the sciences \citet[OTHER CITATIONS]{siepel2019challenges}
% Maybe cite: https://www.biorxiv.org/content/10.1101/092205v3
that investing in
shared community infrastructure produces better results than a
proliferation of individually maintained tools, allowing scientists
to focus on their specific questions rather than software engineering.
\texttt{Msprime} 1.0 is the result of such a community process,
with features added by motivated users, taking advantage of the
established development practices and infrastructure.
% I'm going out on a limb here - do folks agree?
% PLR- personally I have learned SO MUCH, and I'm passing it on to others
Software development in a welcoming community,
with mentorship by experienced developers,
is a hugely useful experience for many users.
The skills that contributors learn
can lead to greatly increased productivity in subsequent
work (e.g., through more reliable code and better debugging skills).
We hope that users who find that
features they require are missing will continue to contribute to
\msprime, leading to a community project that is both high quality
and sustainable in the long term.

@@

\section*{Acknowledgements}
JK is supported by the Robertson Foundation.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
ADK was supported by NIH awards R01GM117241 and R01HG010774.
Franz Baumdicker is funded by the Deutsche Forschungsgemeinschaft
EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
BE was supported by  DFG grant  273887127 through Priority
Programme SPP 1819: Rapid Evolutionary Adaptation (grant STE 325/17-2) to Wolfgang Stephan; BE would also like to acknowledge  funding through The Icelandic Research
Centre (Rann{\'i}s) through an Icelandic Research Fund Grant of  Excellence nr.\ 185151-051 to Einar \'Arnason,  Katr\'in Halld\'orsd\'ottir,  Alison Etheridge,  Wolfgang Stephan, and BE.
